### 2011-11-13 doc/theses/vitasek/appendix-a-jinfer.tex
Minor change - add space
Thesis: ready to send to reviewers.

This appendix will try to describe shortly yet comprehensively \textbf{jInfer} - the Java framework for XML schema inference. Please see project web \cite{jinferweb} for complete information, documentation and download options.

jInfer was developed between 2009 and 2011 at Charles University in Prague as a Software Project by team consisting of Michal Klempa, Mário Mikula, Ro\-bert Sme\-ta\-na, Michal Švirec and Matej Vitásek. The main idea was to create a structure in which all aspects of XML schema inference can be easily implemented and evaluated. The goal was achieved: the SW project was successfuly defended when jInfer was inferring DTD and XSD schemas based on XML documents, old DTD and XSD schemas and XPath queries. Since then, Michal Klempa has successfuly defended his own thesis improving on the grammar simplification process (see below), Michal Švirec has extended the framework with capabilities to detect and repair functional dependencies violation (see \cite{sviro}) and defended his thesis as well. This thesis is the third one based on this framework, and Mário Mikula's is on its way, too.

>>>>

This appendix describes shortly yet comprehensively \textbf{jInfer} - the Java framework for XML schema inference, in which the algorithms described in this work were implemented. Please see project web \cite{jinferweb} for complete information, documentation and download options.

jInfer was developed between 2009 and 2011 at the Charles University in Prague as a Software Project by team consisting of Michal Klempa, Mário Mikula, Ro\-bert Sme\-ta\-na, Michal Švirec and Matej Vitásek. The main idea was to create a structure in which all aspects of XML schema inference can be easily implemented and evaluated. The goal was achieved: the SW project was successfuly defended when jInfer was inferring DTD and XSD schemas based on XML documents, old DTD and XSD schemas and XPath queries. Since then, Michal Klempa has successfuly defended his own thesis improving on the grammar simplification process (see below), Michal Švirec has extended the framework with capabilities to detect and repair functional dependencies violation (see \cite{sviro}) and defended his thesis as well. This thesis is the third one based on this framework, and Mário Mikula's is on its way, too.

### 2011-11-13 doc/theses/vitasek/appendix-c-trace.tex
Thesis: in progress.
Thesis: ready to send to reviewers.

And finally, it is important to know what is the ID/IDREF set recommended by this experiment run - the reason why we do all this! Thus the log is concluded by a CSV formatted list of element - attribute name pairs to be included in the ID and IDREF set, respectively.

@@

Note that in this example trace there were no IDREF AMs found. \qed

>>>>

And finally, it is important to know what is the ID/IDREF set recommended by this experiment run. Thus the log is concluded by a CSV formatted list of element - attribute name pairs to be included in the ID and IDREF set, respectively.

@@

Note that in this example trace there were no \texttt{IDREF} AMs found. \qed

### 2011-11-13 doc/theses/vitasek/chapter-0-preface.tex
Thesis: ready to send to reviewers.

Along with technologies such as SQL/noSQL databases, proprietary binary file formats, plain-text configuration files and JSON, XML is one of the leading formats for storing structured data. However, even though languages such as DTD and XML Schema to describe XML structure exist for a long time, most of the documents use outdated or no schema at all (\cite{1802522}). To tackle this problem one may employ reverse-engineering techniques to infer the schema from existing documents, such as those described in \cite{ahonen, bex, vyhnanovska}. In particular, \cite{archdoc} introduces the jInfer schema inference framework, dealing primarily with the structural parts of the schema: how all the elements, attributes and text data are to be organized in an XML document conforming to that schema. Inference of this kind of structural information was greatly improved in \cite{anti}.\\

@@

The scope of this work is finally limited to the inference of \texttt{ID}/\.\texttt{IDREF}/\.\texttt{IDREFS} from existing XML documents. \texttt{ID} attributes were chosen over \texttt{xs:key} because the preliminary research found that while it is possible to find real-life XML data with schemas containing \texttt{xs:key} structure, schemas with \texttt{ID} attributes are much more common and it is much easier to obtain large data sets for experiments. % TODO something like even the search for ID sets is interesting enough?

\section{Structure of the thesis}

@@

First, we will introduce a few notions required throughout the work, such as XML tree, \texttt{ID} attributes, ID sets, linear programming and the mixed integer problem.

We will then review approaches to ID attribute search from previous articles on this topic and formulate the problem of finding the optimal ID set.

This will lead us to the NP-complete problem of Maximum Independent Set, where we will inspect the approaches to solving it.

@@

An extension to jInfer for finding \texttt{ID} attributes using MIP solver and a combination of heuristics will be presented and experimentally evaluated in the closing chapters.

\section{Conventions}

>>>>

Along with technologies such as SQL/noSQL\footnote{noSQL: collection of non-relational database technologies, \url{http://nosql-database.org/}.} databases, proprietary binary file formats, plain-text configuration files and JSON\footnote{JSON: JavaScript Object Notation, lightweight data format, \url{http://www.json.org/}.}, XML is one of the leading formats for storing structured data. However, even though languages such as DTD and XML Schema\footnote{DTD and XML Schema: 2 most prominent XML schema languages, \cite{Bray:08:EML}} to describe XML structure exist for a long time, most of the documents use outdated or no schema at all \cite{1802522}. To tackle this problem one may employ reverse-engineering techniques to infer the schema from existing documents, such as those described in \cite{ahonen, bex, vyhnanovska}. In particular, \cite{archdoc} introduces the jInfer schema inference framework, dealing primarily with the structural parts of the schema: how all the elements, attributes and text data are to be organized in an XML document conforming to that schema. Inference of this kind of structural information was greatly improved in \cite{anti}.\\

\nomenclature{DTD}{Document Type Definition}

@@

The scope of this work is finally limited to the inference of \texttt{ID}/\.\texttt{IDREF}/\.\texttt{IDREFS} from existing XML documents. \texttt{ID} attributes were chosen over \texttt{xs:key} because the preliminary research found that while it is possible to find real-life XML data with schemas containing \texttt{xs:key} structure, schemas with \texttt{ID} attributes are much more common and it is much easier to obtain large data sets for experiments.

\section*{Structure of the thesis}

@@

In Chapter \ref{chapter-definitions} we introduce a few notions required throughout the work, such as XML tree, \texttt{ID} attributes, ID sets, linear programming and the mixed integer problem.

Then in Chapter \ref{chapter-research}, we review approaches to ID attribute search from previous articles on this topic and formulate the problem of finding the optimal ID set.

This will lead us to the NP-complete problem of Maximum Independent Set, where we will inspect the approaches to solving it in Chapter \ref{chapter-mip}.

@@

An extension to jInfer for finding \texttt{ID} attributes using MIP solver and a combination of heuristics will be presented and experimentally evaluated in Chapter \ref{chapter-experiments}.

\section*{Conventions}

### 2011-11-13 doc/theses/vitasek/chapter-1-definitions.tex
Thesis: ready to send to reviewers.

We shall use the representation introduced in \cite{fidax}, where an XML file is represented by a labeled tree consisting of nodes for elements, attributes and simple text data. This tree shall be called an \textit{XML tree}. For a given node $v$ of an XML tree we define $label(v)$ (name of the node in in the document, only for elements and attributes), $id(v)$ (unique identifier across the document) and $value(v)$ (text content, only for attributes and simple text data) in the same way as the cited article does.

@@

This example introduces an XML file fragment that will be used for demonstration throughout this work. XML tree representing it is in Figure \ref{image-definitions-example-xml-tree}, where each node is annotated with a triple $label(v) : id(v) : value(v)$.

@@

\begin{figure}
  \caption{Example XML Tree}
  \label{image-definitions-example-xml-tree}
  \centering
    \subfigure[XML tree]{\includegraphics[width=.45\textwidth]{images/definitions/xml-tree}}
    \subfigure[Attribute mappings]{\includegraphics[width=.45\textwidth]{images/definitions/xml-tree-ams}}
\end{figure}

@@

According to \cite{Bray:08:EML}, an XML attribute may have the type \texttt{ID}, \texttt{IDREF} or \texttt{IDREFS} (among others). Following constraints are related to these types.

@@

An \texttt{ID} attribute \textsc{must} have a declared default of \texttt{\#IMPLIED} or \texttt{\#REQUIRED}.

@@

\begin{define}[$\Sigma^E$, $\Sigma^A$, $\Sigma$]
	$\Sigma^E$ is the set of all element labels, $\Sigma^A$ is the set of all attribute labels. $\Sigma = \Sigma^E \cup \Sigma^A$ is their union and effectively the set of all labels in the document (simple text data nodes do not have a label).
\end{define}

@@

\paragraph{Example}
The XML tree from Figure \ref{image-definitions-example-xml-tree} has the following non-empty AMs drawn in bold lines: $M_{y}^{a} = \{(2,6), (3,8)\}$, $M_{y}^{b} = \{(2,7)\}$, $M_{y}^{c} = \{(3,9)\}$ and $M_{z}^{a} = \{(5,10)\}$.

Following example equations hold.
\begin{eqnarray*}
\pi_E(M_{y}^{a}) & = & \{2, 3\} \\
\pi_A(M_{z}^{a}) & = & \{10\} \\
\tau(M_{y}^{c}) & = & y
\end{eqnarray*}

@@

\paragraph{Example}
Again referring to the XML tree from \ref{image-definitions-example-xml-tree}, we get the following AM images.
\begin{eqnarray*}
\iota(M_{y}^{a}) & = & \{1, 3\} \\
\iota(M_{y}^{b}) & = & \{2\} \\
\iota(M_{y}^{c}) & = & \{4\} \\
\iota(M_{z}^{a}) & = & \{1\} \\
\end{eqnarray*}

@@

\subsection{\texttt{IDREF} and \texttt{IDREFS} Condition}

@@

From the cited article:
\begin{quote}
The support of attribute mapping $M_x^y$ is the fraction of edges in the XML tree that connect $x$ elements to $y$ attributes.
\end{quote}

@@

Again from the article:
\begin{quote}
The coverage of an attribute mapping measures how much of the image of that mapping occurs elsewhere, as a fraction of all mappings images in the document.
\end{quote}

@@

It is well known that finding the maximum weighted IS is an NP-hard optimization problem, see e.g. \cite{JM1986425}.

@@

The problem of \textit{linear programming} is optimization of a linear function under a set of linear constraints. The formulation is usually called a \textit{linear program}. It can be written in the following form (minimization version is possible too).

@@

Where $\mathbf{x}$ is the vector of variables (to be found by the optimization), $\mathbf{b}$ is the vector and $A$ is the accompanying matrix of constraints and $\mathbf{c}$ is the vector of coefficients for the objective function. $\mathbf{x}$ and $\mathbf{c}$ have length $n$, $\mathbf{b}$ has length $m$ and $A$ has dimensions $m \times n$.

@@

\begin{eqnarray*}
\max_{x} z = \sum_{i=1}^{n} c_i x_i \\
s.t.\, a_{11}x_{1} + a_{12}x_{2} + \ldots + a_{1n}x_{n} & \leqslant & b_{1} \\
	   a_{21}x_{1} + a_{22}x_{2} + \ldots + a_{2n}x_{n} & \leqslant & b_{2} \\
	   \ldots \\
	   a_{m1}x_{1} + a_{m2}x_{2} + \ldots + a_{mn}x_{n} & \leqslant & b_{m} \\
	   x_i \geqslant 0, i = 1, \ldots n \\
\end{eqnarray*}

>>>>

We shall use the representation introduced in \cite{fidax}, where an XML file is represented by a labeled tree consisting of nodes for elements, attributes and simple text data. Parent nodes are connected to child nodes with the edges. This tree shall be called an \textit{XML tree}. For a given node $v$ of an XML tree we define $label(v)$ (name of the node in in the document, only for elements and attributes), $id(v)$ (unique identifier across the document) and $value(v)$ (text content, only for attributes and simple text data) in the same way as the cited article does.

@@

This example introduces an XML file fragment that will be used for demonstration throughout this work. An XML tree representing it is in Figure \ref{image-definitions-example-xml-tree}(a), where each node is annotated with a triple $label(v) : id(v) : value(v)$.

@@

\begin{figure}
  \caption{Example XML Tree}
  \label{image-definitions-example-xml-tree} 
  \centering
    \subfigure[XML tree]{\includegraphics[width=.45\textwidth]{images/definitions/xml-tree}}
    \subfigure[Attribute Mappings]{\includegraphics[width=.45\textwidth]{images/definitions/xml-tree-ams}}
\end{figure}

@@

According to \cite{Bray:08:EML}, an XML attribute may have the type \texttt{ID}, \texttt{IDREF} or \texttt{IDREFS} (among others). The following constraints are related to these types.

@@

An \texttt{ID} attribute \textsc{must} have a declared default of \texttt{\#IMPLIED}\footnote{\texttt{\#IMPLIED} means that the attribute has a specified default value.} or \texttt{\#REQUIRED}\footnote{\texttt{\#REQUIRED} means that the attribute cannot be empty.}.

@@

\begin{define}[$\Sigma^E$, $\Sigma^A$, $\Sigma$]
	$\Sigma^E$ is the set of all element labels, $\Sigma^A$ is the set of all attribute labels. $\Sigma = \Sigma^E \cup \Sigma^A$ is their union and effectively the set of all labels in the document.
\end{define}

@@

\paragraph{Example}
The XML tree from Figure \ref{image-definitions-example-xml-tree}(b) has the following non-empty AMs drawn in bold lines: $M_{y}^{a} = \{(2,6), (3,8)\}$, $M_{y}^{b} = \{(2,7)\}$, $M_{y}^{c} = \{(3,9)\}$ and $M_{z}^{a} = \{(5,10)\}$.

The following example equations hold.
\begin{eqnarray*}
\pi_E(M_{y}^{a}) & = & \{2, 3\} \\
\pi_A(M_{z}^{a}) & = & \{10\} \\
\tau(M_{y}^{c}) & = & y
\end{eqnarray*}

@@

\paragraph{Example}
Again referring to the XML tree from Figure \ref{image-definitions-example-xml-tree}, we get the following AM images.
\begin{eqnarray*}
\iota(M_{y}^{a}) & = & \{1, 3\} \\
\iota(M_{y}^{b}) & = & \{2\} \\
\iota(M_{y}^{c}) & = & \{4\} \\
\iota(M_{z}^{a}) & = & \{1\} \\
\end{eqnarray*}

@@

\subsection*{\texttt{IDREF} and \texttt{IDREFS} Condition}

@@

\begin{quote}
The support of attribute mapping $M_x^y$ is the fraction of edges in the XML tree that connect $x$ elements to $y$ attributes.
\end{quote}

@@

\begin{quote}
The coverage of an attribute mapping measures how much of the image of that mapping occurs elsewhere, as a fraction of all mappings images in the document.
\end{quote}

@@

It is well known that finding the maximum weighted IS is an NP-hard optimization problem, \cite{JM1986425}.

@@

The problem of \textit{linear programming} is optimization of a linear function under a set of linear constraints. The formulation is usually called a \textit{linear program}.

It can be written in the following form (minimization version is possible too).

@@

Where $\mathbf{x}$ is the vector of variables (to be found by the optimization), $\mathbf{b}$ is the vector and $A$ its accompanying matrix of constraints and $\mathbf{c}$ is the vector of coefficients for the objective function. $\mathbf{x}$ and $\mathbf{c}$ have length $n$, $\mathbf{b}$ has length $m$ and $A$ has dimensions $m \times n$. Furthermore, \[\max_{x} f(x)\] means maximize the value of $f(x)$ by changing the value of $x$.\\

@@

\begin{eqnarray*}
\max_{x} z = \sum_{i=1}^{n} c_i x_i \\
s.t. & \\
	   a_{11}x_{1} + a_{12}x_{2} + \ldots + a_{1n}x_{n} & \leqslant & b_{1} \\
	   a_{21}x_{1} + a_{22}x_{2} + \ldots + a_{2n}x_{n} & \leqslant & b_{2} \\
	   \ldots \\
	   a_{m1}x_{1} + a_{m2}x_{2} + \ldots + a_{mn}x_{n} & \leqslant & b_{m} \\
	   x_i \geqslant 0, i = 1, \ldots n \\
\end{eqnarray*}

### 2011-11-13 doc/theses/vitasek/chapter-4-1-experiments-setup.tex
Thesis: ready to send to reviewers.

\chapter{Experiments}

@@

From 3 different sources we collected 6 different data sets, called \dataset{OVA1} - \dataset{OVA3}, \dataset{XMA-c}, \dataset{XMA-p} and \dataset{XMD}. Their summary is Table \ref{table-experiments-data-realistic}, their graph representations can be seen in Figure \ref{image-experiments-data-realistic}. Because the legal status of disclosing these data sets is unclear, we will refrain from identifying them beyond these artificial identifiers. The DVD distributed with this thesis will contain their anonymized version.

@@

We used 2 data sets to convert, \dataset{MSH} and \dataset{NTH}. Unfortunately, the same problem with disclosure as in the previous case applies here, the DVD contains the anonymized version again. None of these sets had any attributes before the conversion. Their summary is Table \ref{table-experiments-data-converted}, their graphs are in Figure \ref{image-experiments-data-converted}.

@@

As soon as we started experimenting with the data coming from the real world, it was obvious that they are not complex enough. After we built the model, we got the most complex graphs of 31 vertices and 47 edges (see Table \ref{table-experiments-data-realistic}). Our solution is to approach the problem from the other side: in the end, we will be solving the equivalent of IS problem on a graph created from XML data. We will create the XML data to contain a more complex graph with a specific number of vertices and edges.

To demonstrate this, consider the following excerpt from an XML file:

@@

Our aim is to create a graph with approximately $v$ vertices and $e$ edges. First, we introduce $v$ elements with names \texttt{vertex0} - \texttt{vertex\{V-1\}}. To constitute an AM, they need an attribute \texttt{attr}, but with large enough random values, so that they do not conflict with others. Second, for each of the $e$ edges we choose two \texttt{vertex*} elements at random, and give them the same value of their \texttt{attr}. This will ensure they cannot share the same ID set, thus effectively creating the edge in the graph representation.

>>>>

\chapter{Experiments}
\label{chapter-experiments}

@@

From 3 different sources we collected 6 different data sets, called \dataset{OVA1} - \dataset{OVA3}, \dataset{XMA-c}, \dataset{XMA-p} and \dataset{XMD}. Their summary is in Table \ref{table-experiments-data-realistic}, their graph representations can be seen in Figure \ref{image-experiments-data-realistic}. Because the legal status of disclosing these data sets is unclear, we will refrain from identifying them beyond these artificial identifiers. The DVD distributed with this thesis will contain their anonymized version.

@@

We used 2 data sets to convert, \dataset{MSH} and \dataset{NTH}. Unfortunately, the same problem with disclosure as in the previous case applies here, the DVD contains the anonymized version again. None of these sets had any attributes before the conversion. Their summary is in Table \ref{table-experiments-data-converted}, their graphs are in Figure \ref{image-experiments-data-converted}.

@@

As soon as we started experimenting with the data coming from the real world, it was obvious that they are not complex enough. After we built the model, we got the most complex graphs of 31 vertices and 47 edges (see Table \ref{table-experiments-data-realistic}). We approach this problem from the other side: in the end, we will be solving the equivalent of IS problem on a graph created from XML data. We will create the XML data to contain a more complex graph with a specific number of vertices and edges.

This data will represent very complex real world schemas with a lot of various attributes with similar values.

Our artificial test data will look similar to the following excerpt from an XML file:

@@

Our aim is to create a graph with approximately $v$ vertices and $e$ edges. First, we introduce $v$ elements with names \texttt{vertex0} - \texttt{vertex\{V-1\}}. To constitute an AM, they need an attribute \texttt{attr}, but with large enough random values, so that they do not conflict with others. Second, for each of the $e$ edges we choose two \texttt{vertex*} elements at random, and give them the same value of their \texttt{attr}. This will ensure they cannot share the same ID set, thus effectively creating the edge in the graph representation.\\

This way we can generate data more complex than anything found in the real world. It will however serve us to measure the performance of our algorithms in extreme cases.\\

### 2011-11-13 doc/theses/vitasek/diplomka.tex
Thesis: in progress.
Minor change - add space
comment out abbrs
Thesis: ready to send to reviewers.

\documentclass[a4paper,12pt,oneside]{report}
\usepackage{graphicx}
\usepackage{color}
\usepackage{url}
\usepackage{subfigure}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{tgpagella}
\usepackage{xstring}
\usepackage{wrapfig}
\usepackage{appendix}
\usepackage{nomencl}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{multicol}
\usepackage[pdfborder=0 0 0]{hyperref}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{complexity}

\newcommand{\myscale}{0.74}
\newcommand{\vect}[1]{\boldsymbol{#1}}
\newcommand{\code}[1]{\texttt{\StrSubstitute{#1}{.}{.\.}}}
\def\.{\discretionary{}{}{}}
\newcommand{\heu}[1]{\texttt{\textit{#1}}}
\newcommand{\dataset}[1]{\texttt{\textit{#1}}}
\newcommand{\jmodule}[1]{\texttt{\textit{#1}}}
\linespread{1.5}

@@

% - make sure all chapter names are in First Caps
% - make sure all references have a name, like Table 4.3.4 instead of just 4.3.4
% - get rid of all short forms: won't -> will not
% - make sure there are no singletons
% - make sure LaTeX does not complaint much about under/overfullness
% - make sure everything is defined and referenced
% - make sure all the heu/data set names are consistent. This holds especially for GLPK (tool) / Glpk (heu) and FIDAX
% - make sure that when referring to heus in algorithms, e.g. when describing how experimental sets are constructed, we correctly refer to their parameters as described in their pseudocodes
% - the official name for things like OVA1 and 100-100 is (test) data set. Make sure I am not calling it files or anything else.
% - make sure labels have consistent names
% - ratio -> FRACTION of XYZ to fix/remove/...
% - what style of quotation marks to use?

@@

Abstrakt: Tato práce navazuje na dřívější pokusy odvodit (inferovat) schému existujících XML dokumentů. Jelikož je odvozování \textit{struktury} již relativně dobře popsáno, soustředíme se na integritní omezení. Několik jich popisujeme, pozornost pak soustředíme na ID/\.IDREF/\.IDREFS atributy z DTD. Na bázi článku od Barbosa a Menelzon stavíme heuristický přístup k problému hledání optimální sady ID atributů, jeho funkčnost a vhodnost pak ověřujeme na škále experimentů.

@@

Abstract: In this work we expand upon the previous efforts to extract (infer) schema information from existing XML documents. We find the inference of \textit{structure} to be sufficiently researched and focus further on integrity constraints. After briefly introducing some of them we turn our attention to ID/\.IDREF/\.IDREFS attributes in DTD. Building on the research by Barbosa and Menelzon we introduce a heuristic approach to the problem of finding optimal ID set. The approach is evaluated and tuned in a wide range of experiments.

@@

\include{chapter-0-preface}

\include{chapter-1-definitions}

\include{chapter-2-research}

\include{chapter-3-mip}

\include{chapter-4-1-experiments-setup}

\include{chapter-4-2-experiments-results}

\include{chapter-5-future}

\include{chapter-6-conclusion}

%%% Seznam použité literatury
\newpage
\nocite{*}
\bibliographystyle{alpha}
\bibliography{literature}

\listoffigures
\addcontentsline{toc}{chapter}{List of Figures}

\listofalgorithms
\addcontentsline{toc}{chapter}{List of Algorithms}

%%% Tabulky v diplomové práci, existují-li.
%\chapwithtoc{List of Tables}
\listoftables
\addcontentsline{toc}{chapter}{List of Tables}

%%% Použité zkratky v diplomové práci, existují-li, včetně jejich vysvětlení.

\printnomenclature[2cm]
\addcontentsline{toc}{chapter}{List of Abbreviations}
\label{chapter-list-abbreviations}

%%% Přílohy k diplomové práci, existují-li (různé dodatky jako výpisy programů,
%%% diagramy apod.). Každá příloha musí být alespoň jednou odkazována z vlastního
%%% textu práce. Přílohy se číslují.

\appendix

\openright
\addcontentsline{toc}{chapter}{Appendices}

\include{appendix-a-jinfer}

\include{appendix-b-iss}

\include{appendix-c-trace}

% TODO a QED square

>>>>

\documentclass[a4paper,12pt,twoside]{report}
\usepackage{graphicx}
\usepackage{color}
\usepackage{url}
\usepackage{subfigure}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{tgpagella}
\usepackage{xstring}
\usepackage{wrapfig}
\usepackage[title,titletoc]{appendix}
%\usepackage{textgreek}
\usepackage{nomencl}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{multicol}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{complexity}
%\usepackage{refcheck}
\usepackage[pdfborder=0 0 0,pdftex,unicode]{hyperref}
\DeclareFontShape{OT1}{cmtt}{bx}{n}{<5><6><7><8><9><10><10.95><12><14.4><17.28><20.74><24.88>cmttb10}{}

\newcommand{\myscale}{0.74}
\newcommand{\vect}[1]{\boldsymbol{#1}}
\newcommand{\code}[1]{\texttt{\StrSubstitute{#1}{.}{.\.}}}
\def\.{\discretionary{}{}{}}
\newcommand{\heu}[1]{\texttt{\textit{#1}}}
\newcommand{\dataset}[1]{\texttt{\textit{#1}}}
\newcommand{\jmodule}[1]{\texttt{\textit{#1}}}
\linespread{1.5}
%\onehalfspacing

@@

% + make sure all chapter names are in First Caps
% + make sure all references have a name, like Table 4.3.4 instead of just 4.3.4
% + get rid of all short forms: won't -> will not
% - make sure there are no singletons
% - make sure LaTeX does not complaint much about under/overfullness
% + make sure everything is defined and referenced
% + make sure there is nothing in the bibliography that is unreferenced
% + make sure all the heu/data set names are consistent. This holds especially for GLPK (tool) / Glpk (heu) and FIDAX
% - make sure that when referring to heus in algorithms, e.g. when describing how experimental sets are constructed, we correctly refer to their parameters as described in their pseudocodes
% - the official name for things like OVA1 and 100-100 is (test) data set. Make sure I am not calling it files or anything else.
% - make sure labels have consistent names
% + ratio -> FRACTION of XYZ to fix/remove/...
% + what style of quotation marks to use? (`` and '')

@@

Abstrakt: Tato práce navazuje na dřívější pokusy odvodit (inferovat) schéma existujících XML dokumentů. Jelikož je odvozování \textit{struktury} již relativně dobře popsáno, soustředíme se na integritní omezení. Několik jich popisujeme, pozornost pak soustředíme na ID/\.IDREF/\.IDREFS atributy z DTD. Na bázi článku od Barbosa a Menelzon (2003) stavíme heuristický přístup k problému hledání optimální sady ID atributů, jeho funkčnost a vhodnost pak ověřujeme na škále experimentů.

@@

Abstract: In this work we~expand upon the previous efforts to~extract (infer) schema information from existing XML documents. We find the~inference of \textit{structure} to~be~sufficiently researched and focus further on~\textit{integrity constraints}. After briefly introducing some of~them we turn our attention to~ID/\.IDREF/\.IDREFS attributes in~DTD. Building on~the~research by~Barbosa and Menelzon (2003) we~introduce a~heuristic approach to~the~problem of~finding optimal ID set. The approach is~evaluated and tuned in~a~wide range of~experiments.

@@

  \include{chapter-0-preface}
  \include{chapter-1-definitions}
  \include{chapter-2-research}
  \include{chapter-3-mip}
  \include{chapter-4-1-experiments-setup}
  \include{chapter-4-2-experiments-results}
  \include{chapter-5-future}
  \include{chapter-6-conclusion}

\newpage
\phantomsection
\addcontentsline{toc}{chapter}{Bibliography}
%\nocite{*}
%\bibliographystyle{alpha}
%\bibliography{literature}
	\include{bibliography}

\newpage
\phantomsection
\addcontentsline{toc}{chapter}{Lists}

\clearpage
\phantomsection
\addcontentsline{toc}{section}{List of Figures}
\listoffigures

\clearpage
\phantomsection
\addcontentsline{toc}{section}{List of Algorithms}
\listofalgorithms

\clearpage
\phantomsection
\addcontentsline{toc}{section}{List of Tables}
\listoftables

\clearpage
\phantomsection
\addcontentsline{toc}{section}{List of Abbreviations}
\label{chapter-list-abbreviations}
\printnomenclature[2cm]

\openright
\clearpage
\phantomsection
\addappheadtotoc
\renewcommand{\appendixname}{Appendix}

\begin{appendices}
  \input{appendix-a-jinfer} % TODO include?
  \include{appendix-b-iss}
  \include{appendix-c-trace}
\end{appendices}
